Insights on ancestry using principal component analysis of genetic data

### 2020-09-21 paper/paper-ancestry-matching.tex
init move code

We use the 1000 Genomes (1000G) Project data \cite[]{10002015global} to infer the ancestry of individuals from a study dataset using the following steps: 1) we project individuals from the study dataset onto the PCA space computed using the 1000G data \cite[]{prive2020efficient}; 2) we compute the robust center and covariance parameters of the Mahalanobis distance \cite[]{prive2020efficient} for each of the 26 populations of the 1000G data; 3) we compute the Mahalanobis distance for each projected individual of the study data and each population of the 1000G data (using the center and covariance parameters computed previously); 4) we derive p-values from those distances, as they are approximately chi-squared distributed with the number of PCs used for computing the distances as degrees of freedom; 5) we affect each individual to the largest corresponding p-value (smallest distance), but discard individuals whose maximum p-value is less than 0.05 (i.e.\ individuals far from every population of the 1000G data).

>>>>

We use the 1000 Genomes (1000G) Project data \cite[]{10002015global} to infer the ancestry of individuals from a study dataset using the following steps: 1) we project individuals from the study dataset onto the PCA space computed using the 1000G data \cite[]{prive2020efficient}; 2) we compute the robust center and covariance parameters of the Mahalanobis distance \cite[]{prive2020efficient} for each of the 26 populations of the 1000G data; 3) we compute the Mahalanobis distance for each projected individual of the study data and each population of the 1000G data (using the center and covariance parameters computed previously); 4) we derive p-values from those distances, as they are approximately chi-squared distributed with the number of PCs used for computing the distances as degrees of freedom; 5) we assign each individual the population group with the largest corresponding p-value (smallest distance), but discard individuals whose maximum p-value is less than 0.05 (i.e.\ individuals far from every population of the 1000G data).
